Make any stupid plot you want

### 2020-09-11 draft/intro.tex
notes from meeting

Why am I starting with DuBois?

@@

The visual channels in fig~\ref{fig:retinal_variable} are recommended based on the measurement type, quantative versus qualitativem  and Munzner generalizes the quantative channels as magnitude channels for ordered attributes (measurements drawn from an ordered set of possible values) and the qualitative channels as identity channels for categorical attributes (random set of possible values).

>>>>

Why am I starting with DuBois? 
Visualization library - spells out/regularizes the ways you can aesthetically encode data, preserving structure of data, scatter - magnitude between values preserved - some ways an accurate representation of the data, concerned w/ as data is changed, graph has to change accordingly, graph needs to change accordingly - owns responsibility for preserving measurement integrity when specified by encodings
    - specify what you want to preserve
        - (choose which) preserve relations in a strict math/set theory sense
    - functional is a good fit b/c it spells out these constraints 
Drawing program - user is responsible for preserving these measurements

@@

The visual channels in fig~\ref{fig:retinal_variable} are recommended based on the measurement type, quantative versus qualitativem  and Munzner generalizes the quantative channels as magnitude channels for ordered attributes (measurements drawn from an ordered set of possible values) and the qualitative channels as identity channels for categorical attributes (random set of possible values). 
topology in measurement types, and that topology informs the channels appropriate for those types:
    quantative continouse, quantative discrete, qualitative catorical ordinal, qualitative categorical
    marks - topology of measurements (people wearing dresses)
    channels - topology of space from which measurements are drawn (possible dress sizes)
    categorical - discrete points w/o anything to do 
    categorical - poset topology?

    base space - topology of observations (people wearing dresses)
    fiber topology - topology of measurements (possible dress sizes)

functional 'cause focus on transforms - if transforms preserve linearity than whole pipeline does. Dev gets guarantee on calling composite.

Add table of which sorts of invariance a channel will preserve
